---
title: "Map Code"
output:
  html_document:
    df_print: paged
---


# 1. Introduction

## a) Goals

## b) Datasets

Most are downloaded from: https://hub.arcgis.com

Canada Land Inventory (soil): see here for more information about classification: https://www.alc.gov.bc.ca/assets/alc/assets/library/agricultural-capability/canada_land_inventory_soil_capability_classification_for_agriculture_1972.pdf

## c) Load packages

```{r}
library(sf)
library(geojsonsf)
library(leaflet)
library(here)
library(tmap)
library(tibble)
library(geojsonio)
library(dplyr)
```

# 2. Import datasets

## a) Provincial boundaries

```{r}
Boundaries <- st_read(here::here("Data/canvec_1M_CA_Admin_shp/canvec_1M_CA_Admin/geopolitical_boundary_1.shp"))
Regions <- st_read(here::here("Data/canvec_1M_CA_Admin_shp/canvec_1M_CA_Admin/geo_political_region_2.shp"))
```

```{r}
tmap_mode("view")

tm_shape(Regions %>% filter(bodt_en == "National")) + tm_sf() +
  tm_shape(Regions %>% filter(juri_en == "Ontario")) + tm_sf(border.col="red")
```
## b) Aboriginal Lands Canada

```{r}
AboriginalLands.sf <- st_read(here::here("Data/Aboriginal_Land_Types_in_Canada/Aboriginal_Lands.shp"))
AboriginalLands.sf <- st_make_valid(AboriginalLands.sf)
#AboriginalLands.sf

#AboriginalLands.Lambers.sf <- st_transform(AboriginalLands.sf, 3978)
#crs_string = "+proj=lcc +lat_1=49 +lat_2=77 +lon_0=-91.52 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs"
#AboriginalLands.new.sf <- st_transform(AboriginalLands.sf, crs_string)
```



```{r}
tmap_mode("view")
Map <- tm_basemap(leaflet::providers$OpenTopoMap, group='Topo')

Map + tm_shape(Regions %>% filter(juri_en == "Ontario")) + 
        tm_sf(border.col="blue", alpha=0) +
tm_shape(AboriginalLands.sf %>% filter(JUR1=="ON")) + 
        tm_sf(col="red", border.col="red") 
```

## c) Land suitability

```{r}
Soil.sf <- st_read(here::here("Data/Soil_Survey_Complex/Soil_Survey_Complex.shp"))
Soil.sf <- st_make_valid(Soil.sf)
Soil.sf$CLI1 <- factor(Soil.sf$CLI1)
```


## d) Native lands: territories, languages, treaties

Downladed from: https://native-land.ca/resources/api-docs/

Instructions: https://native-land.ca/how-to-add-native-land-digital-data-to-your-own-maps/

Territories:

```{r}
Territories.sf <- geojson_sf(here::here("Data/indigenousTerritories.json"))
Drop.id <- c("5ca71dcffa9467840feb51284cecfca5",
             "1c1e61f0b150f96d5f15cfa3e9654567", 
             "994bc739f1b34bc2ffff267e57729825",
             "25716da1cd295e3195ee3cc66dc5b385",
             "25716da1cd295e3195ee3cc66dc5b385",
             "417f7cdb164e68d11261e03dbafe28df",
             "ea7bd2cb60155169501370a0237edf1b",
             "809d847f81e1ea52852092dd74715eb7",
             "1cf5ebccbc3066af4d70aefed5f1d9d1",
             "3850b77372dafc01f1cc8cc05f2484e1")
Territories.sf <- Territories.sf[!is.element(Territories.sf$id, Drop.id),]
Territories.sf <- st_make_valid(Territories.sf)
Territories.sf <- Territories.sf [st_is_valid(Territories.sf),]
#Territories.Lambers.sf <- st_transform(Territories.sf, 3978)
```




Languages:

```{r}
Languages.sf <- geojson_sf(here::here("Data/indigenousLanguages.json"))
Languages.sf <- st_make_valid(Languages.sf)
Languages.sf <- Languages.sf [st_is_valid(Languages.sf),]
Drop.id <- c("278673e8fae9b71f245f619e77beb858",
             "ffedc97df6f020f684ae00eb61d440e9",
             "5f2ba1ba09bd1aca608a229fee20b322",
             "b583d4e5e477a27a553120fbf4fca236",
             "6db2b3e285bde338be1758abb2886221",
             "80e4a5bac9ba0290194e63ba7a179cd4")
Languages.sf <- Languages.sf[!is.element(Languages.sf$id, Drop.id),]
Languages.sf <- st_make_valid(Languages.sf)
Languages.sf <- Languages.sf [st_is_valid(Languages.sf),]
```

Treaties: 

Note: this seems to be incomplete (Robinson-Superior Treaty missing)

```{r}
Treaties.sf <- geojson_sf(here::here("Data/indigenousTreaties.json"))
Treaties.sf <- st_make_valid(Treaties.sf)
Treaties.sf <- Treaties.sf[st_is_valid(Treaties.sf),]
Drop.id <- c("5a2566f01c88ffc1dbf2576ff1d807e3")
Treaties.sf <- Treaties.sf[!is.element(Treaties.sf$id, Drop.id),]
Treaties.sf <- st_make_valid(Treaties.sf)
Treaties.sf <- Treaties.sf[st_is_valid(Treaties.sf),]
```

Crop these layers to North America

```{r}
Bbox <- st_bbox(Treaties.sf)
Bbox[c(1:4)] <- c(-170,7, -50, 84)
```

```{r}
Territories.crop <- st_crop(Territories.sf, Bbox)
Territories.crop <- st_make_valid(Territories.crop)
Territories.crop <- Territories.crop[st_is_valid(Territories.crop),]

Languages.crop <- st_crop(Languages.sf, Bbox)
Languages.crop <- st_make_valid(Languages.crop)
Languages.crop <- Languages.crop [st_is_valid(Languages.crop),]
```

Display


```{r}
tmap_mode("view")
tm_shape(Territories.crop) + tm_sf(col="color", alph=0.3) +
  tm_shape(Languages.crop) + tm_sf(col="color", alph=0.3) +
  tm_shape(Treaties.sf) + tm_sf(col="color", alph=0.3) 
```







## e) Ecoregions

```{r}
Ecoregions.sf <- st_read(here::here("Data/Level_I_Ecoregions_of_North_America/Ecological_Regions_of_North_America___Level_1.shp"))
Ecoregions.sf <- st_make_valid(Ecoregions.sf)
```

## f) Export layers

```{r}
saveRDS(Territories.sf, here::here("Output/R_objects/Territories.sf.rds"))
saveRDS(Soil.sf, here::here("Output/R_objects/Soil.sf.rds"))
saveRDS(AboriginalLands.sf, here::here("Output/R_objects/AboriginalLands.sf.rds"))
saveRDS(Ecoregions.sf, here::here("Output/R_objects/Ecoregions.sf.rds"))

saveRDS(Treaties.sf, here::here("Output/R_objects/Treaties.sf.rds"))
saveRDS(Territories.crop, here::here("Output/R_objects/Territories.crop.rds"))
saveRDS(Languages.crop, here::here("Output/R_objects/Languages.crop.rds"))
```

Dissolve soil map polygons by attribute CLI1

```{r}
Soil.dissolved <- Soil.sf %>% group_by(CLI1) %>% summarize()
Soil.dissolved$CLI1 <- factor(Soil.dissolved$CLI1)
saveRDS(Soil.dissolved, here::here("Output/R_objects/Soil.dissolved.rds"))
```



# 3. Query information for Mississaugas of the Credit

## a) Reserve area

```{r}
Reserve <- AboriginalLands.sf %>% filter(NAME1=="NEW CREDIT INDIAN RESERVE NO. 40A")
```

## b) Soil map within reserve


```{r}
#Soil.crop.Reserve <- st_crop(Soil.sf, st_bbox(Reserve))
```

Get composition of soil types within reserve

```{r}
#Reserve.intersect <- st_intersection(Reserve, Soil.crop.Reserve)
Reserve.intersect <- st_intersection(Reserve, Soil.dissolved)
#Reserve.intersect <- st_make_valid(Reserve.intersect)

#Reserve.intersect$CLI1 <- factor(Reserve.intersect$CLI1, 
#                                 levels=c("0", "1", "2", "3", "4", "5", "6", "7" ,"O" ,"W"))

Result.Reserve <- data.frame(Reserve.ha = sapply(split(st_area(Reserve.intersect), 
                        Reserve.intersect$CLI1), sum, na.rm=TRUE)/(100^2))

```

Repeat for traditional territory

```{r}
Territory <- Territories.sf[grep("Mississaugas of the Credit First Nation", 
                                      Territories.sf$Name, perl=TRUE),]
```

Get composition of soil types within territory

```{r}
#Soil.crop.Territory <- st_crop(Soil.sf, st_bbox(Territory))
Territory.intersect <- st_intersection(Territory, Soil.dissolved)
#Territory.intersect <- st_make_valid(Territory.intersect)
#Territory.intersect$CLI1 <- factor(Territory.intersect$CLI1, 
#                                 levels=c("0", "1", "2", "3", "4", "5", "6", "7" ,"O" ,"W"))

Result.Territory <- data.frame(Territory.ha = sapply(split(st_area(Territory.intersect), 
                                             Territory.intersect$CLI1), sum, na.rm=TRUE)/(100^2))
```

Compare

```{r}
Result.df <- data.frame(CLI1=row.names(Result.Territory), Result.Territory, Result.Reserve)

Result.df <- Result.df %>% 
  mutate(Percent.retained = 100 * Reserve.ha/Territory.ha) %>%
  mutate(Percent.Territory = 100 * Territory.ha/sum(Territory.ha)) %>%
  mutate(Percent.Reserve = 100 * Reserve.ha/sum(Reserve.ha))

Result.df <- rbind(Result.df, NA)
Result.df[nrow(Result.df),1] <- "Total"
Result.df[nrow(Result.df), -1] <- colSums(Result.df[-nrow(Result.df),-1])

Result.df
```
```{r}
Result.df
```


```{r}
tmap_mode("view")
tm_basemap(leaflet::providers$OpenTopoMap, group='Topo') +
  tm_shape(Territory) + tm_sf(border.col="red", alpha=0.1, col="red") +
  tm_shape(Reserve) + tm_sf(col="red") +
  tm_shape(Reserve.intersect) + tm_sf("CLI1") 
```

# 4. Select information from point location

## a) Select territories

Enter a coordinate from google maps: UTM Mississauga campus


```{r}
Coords <- data.frame(lat=43.54859743692376, lon=-79.66263687936457)
Coords.sf <-st_as_sf(Coords, coords = c("lon","lat"), crs=st_crs(Territories.crop))
```

Select polygons that contain location

```{r}
tmp.Territories <- st_join(Coords.sf, Territories.crop)
tmp.Languages <- st_join(Coords.sf, Languages.crop)
tmp.Treaties <- st_join(Coords.sf, Treaties.sf)
```

Display only selected elements: territories

```{r}
tmp.Territories.poly <- Territories.crop %>% 
  filter(is.element(Territories.crop$Name, tmp.Territories$Name))

tmap_mode("view")
tm_basemap(leaflet::providers$OpenTopoMap, group='Topo') +
  tm_shape(tmp.Territories.poly) + tm_sf("color", alpha=0.5, id="Name") 

```

Languages: by location

```{r}
tmp.Languages.poly <- Languages.crop %>% 
  filter(is.element(Languages.crop$Name, tmp.Languages$Name))

tmap_mode("view")
tm_basemap(leaflet::providers$OpenTopoMap, group='Topo') +
  tm_shape(tmp.Languages.poly) + tm_sf("color", alpha=0.5, id="Name") 

```

Treaties: by location (does not print on top of each other?)

```{r}
tmp.Treaties.poly <- Treaties.sf %>% 
  filter(is.element(Treaties.sf $Name, tmp.Treaties$Name))

tmap_mode("view")
Map <- tm_basemap(leaflet::providers$OpenTopoMap, group='Topo') +
  tm_shape(tmp.Treaties.poly) + tm_sf("color", alpha=0.5, id="Name") 

Map

#Map + tm_shape(Coords.sf) + tm_sf("red", size=3)

```

List of territories per location:

```{r}
tmp.Territories$Name
```

Notes:

- We may need a look-up table/database with a nested list, e.g., MCFN < Mississaugas < Anishinabek
- Link to language/cultural groups
- Link to reserves / FNs
- Link to treaties

```{r}
keep <- c(2, 3, 4, 5)
tmp.Territories$Name[keep]
```

```{r}
tmp <- tmp.Territories.poly[keep,] 
tmp$Area  <- st_area(tmp)
tmp <- tmp %>% arrange(desc(Area)) # sort by decreasing area to avoid covering of smaller polygons

tmap_mode("view")
tm_basemap(leaflet::providers$OpenTopoMap, group='Topo') +
  tm_shape(tmp) + tm_sf("color", alpha=0.5, id="Name", border.col="red") 

```


For selecting multiple features of the same/different layer by clicking on a map:

https://gis.stackexchange.com/questions/430074/displaying-pop-ups-for-overlapping-polygons-in-the-same-layer-in-leaflet





Example: list of reserves in Ontario

```{r}
AboriginalLands.sf %>% filter(ALTYPE=="Indian Reserve", JUR1=="ON") %>% 
  pull(NAME1) %>% unique() %>% sort()
```


```{r}
Territories.crop$Area <- st_area(Territories.crop)

#View(Territories.crop %>% arrange(desc(Area)))
```

